Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/Motiv.tex
sec. 2 is modified

Our overall goal is to 
(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of \Sadegh{an additional bounded
disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);}
and at the same time
%\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
(ii) to minimize the total number of bits that are required for storing the explicit controller 
while ensuring the implementation error $e\leq \Delta$ is satisfied by the implementation.

@@

 \Sadegh{
For our example, we choose $\Delta_0=0$ and $\mathcal W = \{0\}$. 
We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$.
Next, we ask Daisy
to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
at all points in the control domain, the difference between the infinite-precision controller function
and its mixed-precision implementation is at most $\Delta_0$.
}

\Sadegh{
Unfortunately, $\Delta_0=0$ is not realizable, as the implementation error is always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
%\eva{Is this the error due to mixed-precision or due to wrong regions?}
Therefore, we define $\Delta_1 := \Delta_0 + \delta$ with $\delta$ being a fixed threshold (we chose $\delta = 0.05$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
shown in Figure~\ref{fig:inverted_pendulum}(b).
The controller has \RM{XX} regions.
\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps} 
}

Next, we ask Daisy to provide us with mixed-precision implementation for all the parameters and to compute a static bound on the
implementation error. 
The mixed-precision scheme given by Daisy results in an implementation with $6084$ bits in total 
for the corresponding robust explicit MPC.
Daisy also computes a static error bound of \RM{what?}
Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
and return this implementation.
The mixed-precision implementation takes about $10\%$ less memory compared 
to the smallest uniform precision implementation that respects $\Delta_1$,
and about $XXX\%$ \RM{what} less memory than an implementation that uniformly uses
32 bits.

	\tikzstyle{block} = [draw, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw,  circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	\begin{figure*}[t]
		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
			\centering
			\node [block,scale=1,,text width=3.5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
			node distance=1cm] (RMPC) {Robust explicit MPC design (computed by MATLAB)};
			%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
			\node [block, scale=1,right=2.5cm of RMPC,
			node distance=5cm,text width=4cm] (mixed) {Finite precision implementation (computed by Daisy)};
			\node [draw, diamond, 
			minimum height=3em, minimum width=3em, right =1cm of mixed,
			node distance=5cm] (decide) {$e\leq \bar \Delta$};
			\node [block, right of=decide,
			node distance=3cm] (done) {Done};
			\node [block, below of= decide,
			node distance=3cm] (delta) {increase $\Delta$};
			\node [scale=1] at (3,-.25)  {
				$u(x)=Kx+v$
			};
		\node at (9,-.25) {$e$};

			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
			\draw [->] (mixed) -- node [name=aaa] {}(decide);
			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
			\draw [->] (decide) -- node[pos=0.99] {} 
			node [] {No} (delta);
			\draw [->] (delta) -| node [above] {} (RMPC);

	\end{tikzpicture}
	\caption{high-level description of the proposed memory-efficient robust MPC design
\RM{what is $\bar{\Delta}$}
\RM{try to draw a better picture spanning only one column. the information in this pic is sparse}
\RM{why is $u$ a single affine map?}
\RM{why is Daisy only giving $e$? Shouldn't it also return the best mixed precision impl?}
}
	\label{fig:overview}
\end{figure*}

>>>>

Our overall goal is to 
(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of \Sadegh{an additional bounded
disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);}
and at the same time
%\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
(ii) to minimize the total number of bits that are required for storing the explicit controller.

@@

 \Sadegh{
For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. Over the computed controller, we compute the error due to incorrect region selection $e$ and in case that $e<\Delta$, we ask Daisy
to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
at all points in the control domain, the difference between the infinite-precision controller function
and its mixed-precision implementation is at most $\Delta_0$.
}

\Sadegh{
Unfortunately, $\Delta_0=0$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
%\eva{Is this the error due to mixed-precision or due to wrong regions?}
Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
shown in Figure~\ref{fig:inverted_pendulum}(b).
The controller has $14$ regions.
\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps} 
}
%\begin{equation}
%\kappa(x_k)=
%\begin{cases}
%.05x_k-9.67 & \text{if $x_k\in \mathcal{R}_1$}\\
%F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
%\vdots\\
%F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
%\end{cases} 
%\end{equation}

Next, we ask Daisy to provide us with mixed-precision implementation for all the parameters and to compute a static bound on the
implementation error. 
The mixed-precision scheme given by Daisy results in an implementation with $6084$ bits in total 
for the corresponding robust explicit MPC.
Daisy also computes a static error bound of $0.03$.
Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
and return this implementation.
The mixed-precision implementation takes about $10\%$ less memory compared 
to the smallest uniform precision implementation that respects $\Delta_1$,
and about $57\%$ less memory than an implementation that uniformly uses
32 bits.

\tikzstyle{block} = [draw, rectangle, 
minimum height=4em, minimum width=6em]
\tikzstyle{block2} = [draw, rectangle, 
minimum height=1em, minimum width=4em]
\tikzstyle{sum} = [draw,  circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
\begin{figure}[t]
	\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
	\centering
	\node [block,scale=1,,text width=5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
	node distance=1cm] (RMPC) {Robust explicit MPC design};
	%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
	\node [block, scale=1,below=2.5cm of RMPC,
	node distance=5cm,text width=5cm] (Uij) {Point location error computation};
	\node [draw, diamond, 
	minimum height=3em, minimum width=3em, below =1cm of Uij,
	node distance=5cm] (decide) {$e\leq  \Delta$};
	\node [block, below=1cm of decide,node distance=3cm] (done) {Mixed-precision implementation};
	\node [block2, right=2cm of decide,
	node distance=3cm] (delta) {Increase $\Delta$};
	\node [block,below of= done] (output) {Low-precision controller};
	%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
	\node at (9,-.25) {$e$};

	\draw [draw,->] (RMPC) -- node [left] {high-precision controller}(Uij);
	\draw [->] (Uij) -- node [left] {$e$}(decide);
	\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
	\draw [->] (decide) -- node[pos=0.99] {} 
	node [] {No} (delta);
	\draw [->] (delta) |- node [above] {} (RMPC);
	\draw [->] (done) -- node [above] {} (output);

	\node [block2, scale=1] at (1.885,-.42) {MATLAB} ;
	\node [block2, scale=1] at (1.97,-4.18) {Daisy} ;
	\node [block2, scale=1] at (1.58,-8.84) {Daisy} ;
	\end{tikzpicture}
	\caption{high-level description of the proposed memory-efficient robust MPC design}
	\label{fig:overview}
\end{figure}

%	\tikzstyle{block} = [draw, rectangle, 
%	minimum height=3em, minimum width=6em]
%	\tikzstyle{sum} = [draw,  circle, node distance=1cm]
%	\tikzstyle{input} = [coordinate]
%	\tikzstyle{output} = [coordinate]
%	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
%	\begin{figure*}[t]
%		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
%			\centering
%			\node [block,scale=1,,text width=3.5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
%			node distance=1cm] (RMPC) {Robust explicit MPC design (computed by MATLAB)};
%			%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
%			\node [block, scale=1,right=2.5cm of RMPC,
%			node distance=5cm,text width=4cm] (mixed) {Finite precision implementation (computed by Daisy)};
%			\node [draw, diamond, 
%			minimum height=3em, minimum width=3em, right =1cm of mixed,
%			node distance=5cm] (decide) {$e\leq \bar \Delta$};
%			\node [block, right of=decide,
%			node distance=3cm] (done) {Done};
%			\node [block, below of= decide,
%			node distance=3cm] (delta) {increase $\Delta$};
%			\node [scale=1] at (3,-.25)  {
%				$u(x)=Kx+v$
%			};
%		\node at (9,-.25) {$e$};
%			
%			
%			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
%			\draw [->] (mixed) -- node [name=aaa] {}(decide);
%			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
%			\draw [->] (decide) -- node[pos=0.99] {} 
%			node [] {No} (delta);
%			\draw [->] (delta) -| node [above] {} (RMPC);
%	
%	\end{tikzpicture}
%	\caption{high-level description of the proposed memory-efficient robust MPC design
%\RM{what is $\bar{\Delta}$}
%\RM{try to draw a better picture spanning only one column. the information in this pic is sparse}
%\RM{why is $u$ a single affine map?}
%\RM{why is Daisy only giving $e$? Shouldn't it also return the best mixed precision impl?}
%}
%	\label{fig:overview}
%\end{figure*}
